\documentclass{report}
\usepackage[hmargin=3cm,vmargin=3.5cm]{geometry}
\usepackage{multirow}
\usepackage{outlines}
\begin{document}
\title{Automatic Importance Estimation in  \\
         Forward Monte Carlo Calculations}
\author{Thomas E. Booth}
\date{\today}
% \maketitle
\setcounter{secnumdepth}{0}
\section{Automatic Importance Estimation in Forward Monte Carlo Calculations}
\subsection{Introduction}
\begin{outline}
 \1 Applying splitting and roulette involves knowledge of the importance function
 \1 Splitting can be geometric, space- or energy- dependent. 
 \1 Weight windows have an upper and lower bound for a particles weight and can be used for VR. 
 \1 parameters specified by user rises significantly with each degree of freedom. 
 \1 Space and energy (WW) splitting yields two to five times better calculational efficiency than geometry splitting. 
\end{outline}
\subsection{Importance Generator Theory}
\begin{outline}
 \1 Importance = expected score particle will generate in tally. 
 \1 Importance = total score due to particles leaving cell/ weight leaving the cell
 \1 Generator requires adequate sample size leaving the cell. 
 \1 Zero variance solution = every history contributes the same score
 \1 WW inversely proportional to variance.
   \2 WW is chosen so that track weight*expected score (per unit track rate) = constant. 
\end{outline}
\subsection{Conclusions}
\begin{outline}
 \1 Importance generator is well-optimized after 2 trial runs. 
 \1 User can see the importance regions of the problem too. 
\end{outline}
\end{document}
